Reaction-diffusion spatial modeling of COVID-19 in Chicago

### 2021-07-25 draft/chicago-spatial-covid-draft.tex
Include updated initial conditions and optimal parameters

\begin{savenotes}
\begin{table}[h]
	\centering
	\caption{ODE parameters}
	\label{tab:parameters}
	\begin{tabular}{ c c c c }
		\hline
		\hline
			&	&	Optimal	&	Initial value \\
		\hline
		Population	&	$N$	&	2,695,598 \\
		Initial population	&	$I_0$	&	 \\
		Transmission rate, $S \rightarrow I$ [per day]	&	$\beta$\footnote{The transmission rate $\beta$ must be divided by $N$ when used in the ODE model.}	&	&	$c \in U[0,1]$ \\
		Transition rate, $I \rightarrow R$ [per day]	&	$\gamma$	&		&	$c \in U[0.25,0.75]$ \\
		Diffusivity, $S$ [km$^2$/day]	&	$\D_S$	&	10	&	\\
		Diffusivity, $I$ [km$^2$/day]	&	$\D_I$	&	100	&	\\
		\hline
		\hline
	\end{tabular}
\end{table}
\end{savenotes}

>>>>

\begin{savenotes}
\begin{table}[h]
	\centering
	\caption{ODE parameters}
	\label{tab:parameters}
	\begin{tabular}{ c c c c }
		\hline
		\hline
			&	&	Median (interquartile range)	&	Initial value \\
		\hline
		Population	&	$N$	&	2,695,598 \\
		Initial population	&	$(I_0, R_0)$	&	(127, 2) \\
		Transmission rate, $S \rightarrow I$ [per day]	&	$\beta$\footnote{The transmission rate $\beta$ must be divided by $N$ when used in the ODE model.}	&	0.38206(0.38204-0.38209)	&	$c \in U[0,1]$ \\
		Transition rate, $I \rightarrow R$ [per day]	&	$\gamma$	&	 0.39656(0.39654-0.39659)	&	$c \in U[0.25,0.75]$ \\
		Diffusivity, $S$ [km$^2$/day]	&	$\D_S$	&	10	&	\\
		Diffusivity, $I$ [km$^2$/day]	&	$\D_I$	&	100	&	\\
		\hline
		\hline
	\end{tabular}
\end{table}
\end{savenotes}
